### 2016-07-07 image_setup.tex
Testing image setup. More new info

It is possible that the testbed administrator requires to add other
scripts to configure the \ac{Raspi}s besides the ones introduced here.
This would be tedious to distribute to all \ac{Raspi}s at a later stage.
We ease this task by making the \ac{Raspi}s fetch all the configuration
scripts during start up from a \texttt{.zip} file before running the
configuration scripts. The below script attempts to download/update the
scripts:

>>>>

Besides the scripts introduced up to this point of our procedure, it is
possible that the testbed administrator requires to add other scripts to
configure its \ac{Raspi}s. We ease this task by making the \ac{Raspi}s
fetch all the configuration scripts during start up from a \texttt{.zip}
file before running the configuration scripts. The role of this script
is the same as theThe below script attempts to download/update the
scripts:
